---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# ecods

<!-- badges: start -->
<!-- badges: end -->

## Overview
ecods aims to streamline the preparation of ecological desk studies for projects in England. It does this by scraping information from Natural England's [geodata portal](https://naturalengland-defra.opendata.arcgis.com/). For a site of interest the package returns data on designated sites, ancient woodland and priority habitats. It also returns the Local Planning Authority and National Character Area in which the site is located.

The designated sites currently queried are:

- SPA
- SAC
- Ramsar
- SSSI
- NNR
- AONB (now called National Landscapes)
- National Parks
- LNRs

## Installation
The package can be installed from Digital Ecology's Codeberg repository:
```{r, eval = FALSE}
remotes::install_git("https://codeberg.org/Digital-Ecology/EcoDS_Package.git")
```

## Usage

The main function in the package is the `ecods()` function. This creates buffers around an input site, and returns an sf object with the sites that intersect those buffers. The package has an example site to demonstrate the function.
```{r, message = FALSE, warning = FALSE}
library(ecods)

site <- sf::st_transform(sample_site_boundary, 4326)

ecods(site)
```

The Local Planning Authority or National Character Area functions return just the name of the area as a string:
```{r, message = FALSE}
fetch_lpa(site)

fetch_nca(site)
```

## Bugs
If you encounter a bug, please file an issue with a minimal reproducible example on [Codeberg](https://codeberg.org/Digital-Ecology/EcoDS_Package/issues).

## Code of Conduct
This project is released subject to a [Contributor Code of Conduct](https://www.contributor-covenant.org/version/2/1/code_of_conduct/). By participating in the project you agree to bide by its terms.
